---
title: "Researcher Mentoring Program for Early-Career Researchers (2026)" 
subtitle: "Application Details & Information for Matching"
# author: "Jen Beaudry"
date: "December 2025"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \renewcommand{\arraystretch}{1.4} #adds whitespace to all tables
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE, 
                      fig.path = here::here("figs"))

options(knitr.duplicate.label = "allow") # use this when you use the child files
```


```{r run eligibility check, child = (here::here("01_analysis_pre_matching", "02_mentoring_eligibility_check_26.Rmd"))}

```


```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

```

```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)

```

```{r load data, include=FALSE}

# these files include eligible folks, with eligibility status indicated in the file
# row.names gets rid of the first column from the dataframe.
# [breadcrumb -- do I need all of these datafiles for this?]

# mentor data

df_tor <- read_csv(here::here("00_data", "processed_data", "eoi_mentor_eligible.csv"), 
                   lazy = FALSE)

mentor_areas_wide <- read_csv(here::here("00_data", "processed_data", "eoi_mentor_areas_wide.csv"), 
                   lazy = FALSE)

# mentee data

df_tee <- read_csv(here::here("00_data", "processed_data", "eoi_mentee_eligible.csv"), 
                   lazy = FALSE)


mentee_areas_wide <- read_csv(here::here("00_data", "processed_data", "eoi_mentee_areas_wide.csv"), 
                   lazy = FALSE)

# mentees and mentors combined

df <- read_csv(here::here("00_data", "processed_data", "eoi_combined_eligible.csv"), 
                   lazy = FALSE)

# load metadata for mentor

meta_tor <- read_csv(here::here("00_data", "raw_data", "metadata_eoi_mentor.csv"), lazy = FALSE) %>%
  filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables

# load metadata for mentee

meta_tee <- read_csv(here::here("00_data", "raw_data", "metadata_eoi_mentee.csv"), lazy = FALSE) %>%
  filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables

```

\newpage

```{r area descriptions table}

## mentees 

meta_areas_tee <- meta_tee %>%
  filter(scale == "areas") %>%
  select (c(new_variable, item_text_short))

meta_areas_tee %>%
  knitr::kable (format = "latex", booktabs = T, linesep = "",
  col.names = c("Area", "Brief description"),
  caption = "Description of Areas for Development",
  align = 'll'
  ) %>%
  column_spec(2, width = "4in") %>%
  styler_pdf()

# redundant to include areas from mentors

# meta_areas_tor <- meta_tor %>% 
#   filter(scale == "areas") %>% 
#   select (c(new_variable, item_text_short))
# 
# meta_areas_tor %>% 
#   knitr::kable (booktabs = T, linesep = "\\addlinespace",
#   col.names = c("Area", "Brief description"),
#   caption = "Description of Areas for Development", 
#   align = 'll'
#   ) %>%
#   column_spec(2, width = "4in") %>% 
#   styler_pdf()


```

\newpage

```{r areas for mentors table}

total_tor <- nrow(mentor_areas_wide)

mentor_areas_wide %>% 
  select(c(name, college, level_recode, areas)) %>% 
  arrange(name) %>% 
knitr::kable (format = "latex", booktabs = T, linesep = "",
              col.names = c("Mentor", "College", "Level", "Areas to Mentor"), 
              caption = 
                sprintf("Areas of Interest by Mentor (n = %d)",
                                total_tor), 
              align = 'lccl', 
              longtable = T)  %>% #break the table over multiple pages
  column_spec(1, width = "1in") %>% 
  column_spec(2, width = "1.5in") %>% 
  column_spec(3, width = "1in") %>% 
  column_spec(4, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 

```

\newpage 

```{r areas for mentees table}

total_tee <- nrow(mentee_areas_wide)

mentee_areas_wide %>% 
  select(c(name, college, level_recode, areas)) %>% 
  arrange(name) %>% 
knitr::kable (format = "latex", booktabs = T, linesep = "",
              col.names = c("Mentee", "College", "Level", "Areas for Growth"), 
              caption = 
                sprintf("Areas of Interest by Mentee (n = %d)",
                                total_tee), 
              align = 'lccl', 
              longtable = T)  %>% #break the table over multiple pages
  column_spec(1, width = "1in") %>% 
  column_spec(2, width = "1.5in") %>% 
  column_spec(3, width = "1in") %>% 
  column_spec(4, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 

```

\newpage

```{r names by area for mentors table}

# make the data long again....

names_long <- df %>% 
  select (-c(`first_name`:title, work_phone:contract_end_date, why_mentor:mentoring_approach)) %>% 
  pivot_longer(
    cols = planning:other_2,
    names_to = "areas", 
    values_to = "rank"  
               )

# recode the ranks to yes or NA for interest

names_long2 <- names_long %>% 
  mutate(interest = ifelse(rank %in% NA, NA, "yes")) 

# select relevant data for all
names <- names_long2 %>% 
  select (c(id,`name and college`, name, college, level_recode, areas, rank, interest, role)) %>% 
  filter(interest == "yes")

# make this wide again and combine all of the names into one cell. # do only for mentors
names_wide_tor <- names %>% 
  filter(role == "mentor") %>% 
  select (-c(`name and college`, rank)) %>% 
  pivot_wider(id_cols = "areas", names_from = "id", values_from = name)

# combine the areas into one column
names_wide_tor2 <- names_wide_tor %>% 
  unite ("names", starts_with("mentor_"), sep = ", ", remove = FALSE, na.rm = TRUE) %>% 
  arrange(areas)


names_wide_tor2 %>% 
  select(c(areas, names)) %>% 
knitr::kable (format = "latex", booktabs = T, linesep = "",
              col.names = c("Areas", "Interested Mentors"), 
              caption = 
                sprintf("Mentors by Areas of Interest (n = %d)",
                        total_tor),
              align = 'll', 
              longtable = T)  %>% #break the table over multiple pages
  column_spec(1, width = "1.5in") %>% 
  column_spec(2, width = "4.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 

```

\newpage

```{r names by area for mentees table}

# use the `names by area for mentors` long data and filter for mentees

# make this wide again and combine all of the names into one cell. # do only for mentees
names_wide_tee <- names %>% 
  filter(role == "mentee") %>% 
  select (-c(`name and college`, rank)) %>% 
  pivot_wider(id_cols = "areas", names_from = "id", values_from = name)


# combine the areas into one column
names_wide_tee2 <- names_wide_tee %>% 
  unite ("names", starts_with("mentee_"), sep = ", ", remove = FALSE, na.rm = TRUE) %>% 
    arrange(areas)


names_wide_tee2 %>% 
  select(c(areas, names)) %>% 
knitr::kable (format = "latex", booktabs = T, linesep = "",
              col.names = c("Areas", "Mentees"), 
              caption = 
                sprintf("Mentees by Areas for Growth (n = %d)", 
                        total_tee),
              align = 'll', 
              longtable = T)  %>% #break the table over multiple pages
  column_spec(1, width = "1.5in") %>% 
  column_spec(2, width = "4.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 


```


```{r output names for colleges, eval = FALSE}

# use this to send the list of names to the colleges

# BGL

bgl_tee <- df_tee %>% filter(str_detect(college, "Business")) %>% select(name)
bgl_tor <- df_tor %>% filter(str_detect(college, "Business")) %>% select(name)

# EPSW

epsw_tee <- df_tee %>% filter(str_detect(college, "Education")) %>% select(name)
epsw_tor <- df_tor %>% filter(str_detect(college, "Education")) %>% select(name)

# HASS

hass_tee <- df_tee %>% filter(str_detect(college, "Humanities")) %>% select(name)
hass_tor <- df_tor %>% filter(str_detect(college, "Humanities")) %>% select(name)

# mph

mph_tee <- df_tee %>% filter(str_detect(college, "Medicine")) %>% select(name)
mph_tor <- df_tor %>% filter(str_detect(college, "Medicine")) %>% select(name)

# NHS

nhs_tee <- df_tee %>% filter(str_detect(college, "Nursing")) %>% select(name)
nhs_tor <- df_tor %>% filter(str_detect(college, "Nursing")) %>% select(name)

# SE

se_tee <- df_tee %>% filter(str_detect(college, "Engineering")) %>% select(name)
se_tor <- df_tor %>% filter(str_detect(college, "Engineering")) %>% select(name)


```


```{r number_of_mentees_per_area, eval=TRUE}

meta_areas_tee <- meta_tee %>% 
  filter (scale == "areas") %>% 
  rename(areas = new_variable)

# of those applied and were eligible, this is what they expressed interest in

count_tee <- names %>% 
    filter(role == "mentee") %>% 
  group_by(areas) %>% 
  summarise(n = n())


count_with_des <- right_join(meta_areas_tee, count_tee, by = "areas") %>% 
  select(item_text_short, n) %>% 
  arrange(-n)

```

\newpage
We explored how many mentees indicated that they wanted to be 
mentored in various areas of need (see Table \ref{tab:number_of_mentees_per_area_table}). '`r count_with_des[1,1]`' was the most common area of interest 
whereas '`r count_with_des[21,1]`' was a more niche area of need. 


```{r number_of_mentees_per_area_table, eval=TRUE}

count_with_des %>% 
  knitr::kable (format = "latex", booktabs = T, linesep = "",
  col.names = c("Area for mentoring", "Number of mentees"),
  caption = 
    sprintf("Number of eligible mentees (n = %d) who wanted to be mentored in different areas", 
              total_tee),
  align = 'lc'
  ) %>%
  column_spec(1, width = "4in") %>% 
  styler_pdf()


```

\newpage

```{r number_of_mentors_per_area, eval=TRUE, include=TRUE}

meta_areas_tor <- meta_tor %>% 
  filter (scale == "areas") %>% 
  rename(areas = new_variable)

# of the those who applied and were eligible, these are the areas they could provide mentoring in

count_tor <- names %>% 
    filter(role == "mentor") %>% 
  group_by(areas) %>% 
  filter(!(areas %in% "other_1")) %>% 
  filter(!(areas %in% "other_2")) %>% 
  summarise(n = n())


count_with_des <- right_join(meta_areas_tor, count_tor, by = "areas") %>% 
  select(item_text_short, n) %>% 
  arrange(-n)

```

We also explored the number of mentors who could provide mentoring in different
areas (see Table \ref{tab:number_of_mentors_per_area_table}). 
'`r count_with_des[1,1]`' was the most common area of 
potential mentoring support whereas '`r count_with_des[21,1]`' was a more niche 
area of support. 

```{r number_of_mentors_per_area_table, eval=TRUE, include=TRUE}

count_with_des %>% 
  knitr::kable (format = "latex", booktabs = T, linesep = "",
  col.names = c("Area for mentoring", "Number of mentors"),
  caption = 
    sprintf("Number of eligible mentors (n = %d) who could provide mentoring in different areas", 
              total_tor),
  align = 'lc'
  ) %>%
  column_spec(1, width = "4in") %>% 
  styler_pdf()


```



```{r code graveyard, eval = FALSE}

# rearrange the columns!

names <- names %>%
  relocate (`voted ranks`, .after = `Potential Names`) %>%
  relocate (`mean`, .after = last_col())


kable(names, align = c('l', 'c', 'c', 'c', 'l'), 
      col.names = c("Potential Names", "Voted Ranks", "Sum", "Num of Votes", "Mean")) %>% 
        column_spec (column = 4, width = "1.5cm")


bgl_tor_details <- df_tor %>% 
  filter (college == "Business, Government and Law") %>% 
  select(c(name, level_recode))

bgl_tor_details %>% 
knitr::kable (booktabs = T, linesep = "",
              col.names = c("Name", "Level"), 
              caption = "Mentors in Business, Government and Law",
              align = 'lcc') %>% 
     styler_pdf() 


epsw_tor_details <- df_tor %>% 
  filter (college == "Education, Psychology and Social Work") %>% 
  select(c(name, level_recode))

epsw_tor_details %>% 
knitr::kable (booktabs = T, linesep = "",
              col.names = c("Name", "Level"), 
              caption = "Education, Psychology and Social Work",
              align = 'lcc') %>% 
     styler_pdf() 

df_tor %>% 
  select(c(college, name, level_recode)) %>% 
    group_by(college) %>% 
  mutate(perc = round(100*(n / sum(n)),2)) %>% 
  arrange(college) %>% 
  ungroup



# pack_rows seemingly does not work with long data. I need to figure out a different way of doing this...
# 
# knitr::kable (
#   areas_tor[, c(2,3)], # select only the areas interest and ranks column [you need at least two columns!]
#   booktabs = T,
#   linesep = "",
#   col.names = c("Names", "Ranks of Interests (if applicable)"),
#   caption = "Areas of interest by mentors",
#   longtable = T #break the table over multiple pages
#   ) %>%
#   pack_rows (index = table(areas_tor$`name and college`)) %>%
#   kable_styling(full_width = F, 
#                 latex_options = c("repeat_header", "hold_position", "striped")) 
# # use different styling to repeat the header

```

If you have any questions, please contact Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in Research Development and Support. 